\subsection{Evaluation}

We evaluated the system on three axes: correctness, usability (end-to-end integration), and basic performance.

\subsubsection{Correctness}
We use automated tests to validate the constraints and semantics of the solver encodings and their Python integration:
\begin{itemize}
    \item \textbf{Constraint correctness}: no repeated \texttt{player\_id} in a line/pair, and correct position-group filtering.
    \item \textbf{Combo semantics}: attribute matching (team/nationality/event), symmetry breaking, and multi-combo activation on the same line/pair.
    \item \textbf{Reward arithmetic}: effective totals are consistent with activated rewards (e.g., \texttt{salary\_eff = base\_salary - total\_SAL\_bonus}).
    \item \textbf{API contract stability}: responses can be parsed into typed models and contain all required fields.
\end{itemize}

\subsubsection{End-to-End Demo Validation}
We verify the complete pipeline by running the backend and invoking the optimization endpoints and the demo artifact endpoints. This checks that:
\begin{itemize}
    \item SQLite data loads successfully.
    \item The solver can be executed from within the backend process.
    \item The frontend can retrieve and render results using the published JSON contract.
\end{itemize}

\subsubsection{Performance}
We report basic solver runtimes for representative queries:
\begin{itemize}
    \item Goal 1 Stage A: time per abstract-template solve.
    \item Goal 1 Stage B: time to enumerate top-$N$ grounded solutions for a fixed template.
    \item Goal 2: response time for interactive requests under typical user constraints.
\end{itemize}
All measurements were taken on commodity laptop hardware and are sufficient for an interactive demo; further optimization (incremental solving, caching, and tighter candidate filtering) is left as engineering work.
